%!TEX root = ../../presentation.tex

\section{Introduction}
 
\begin{frame}
    \frametitle{Motivation}
    
    \begin{outline}
        \1 Efficient Market Hypothesis (EMH)
        \1 Option Mining
        \1 Twitter as source
    \end{outline}
\end{frame}

\note[itemize]{
    \item EMH: News aren't predictable $\rightarrow$ random walk
    \item New millennium: At least predictable behavioral and psychological elements
    \item Option mining: Big data approach
    \item Why Twitter: Later
}

\begin{frame}
    \frametitle{Research Question}

    \emph{
    To what extent can stock market movements be explained by the public opinion extracted from Twitter?
    }
\end{frame}

\begin{frame}
    \frametitle{Research Goals I}
    
    \begin{outline}
        \1 Determine companies, keywords and stock symbols to analyze
            \2 Which companies should be analyzed?
            \2 Which keywords should be used to find corresponding tweets?
            \2 Which company uses which stock symbol in order to retrieve share prices?
    \end{outline}
\end{frame}

\begin{frame}
    \frametitle{Research Goals II}

    \begin{outline}

    \1 G2 - Gather tweets and their sentiments and stock prices
        \2 Why Twitter and not any other social media platform?
        \2 In which way can tweets be collected?
        \2 In which way can sentiments be determined?
        \2 Which sentiments are present for various companies?

    \1 G3 - Comparing sentiment time series with share prices
        \2 Can the time series of sentiments explain the share prices?

    \end{outline}
\end{frame}