%!TEX root = ../main.tex

\chapter{Introduction}
\label{c:introduction}

% \section{Section Title}
% \subsection{Subsection}
% \subsubsection{Subsubsection}
% \paragraph{Paragraph}
% \subparagraph{Subparagraph}

% \ul = underline
% \st = strikethrough
% \hl = highlight
% \textbf = bold face
% \textit = italic face
% \textsl = slanted
% \textsf = sans serif

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This chapter provides an introduction to this thesis.
In \cref{s:introduction-motivation} the general motivation is discussed.
The section is followed by outlining the research goals in \cref{s:introduction-researchgoals}.
\Cref{s:introduction-researchmethodology} gives an insight into research methods used in order to answer the raised research questions.
Finally, \cref{s:introduction-structureofthisthesis} gives an outlook of the structure of the remaining thesis.

\section{Motivation}
\label{s:introduction-motivation}

Many studies have been published which try to predict the stock market movement \citep[see][]{Bollen2011a,Mittal2012a,Nguyen2015a,Pagolu2016a,Zhang2011a}.
The \ac{EMH} states that financial market movements depend on news, current events and product releases and all these factors will have significant impact on a company's stock value
\citep{fama1965behavior}.
Due to the fact that news and current events are unpredictable, stock market prices follow a random walk pattern and cannot be predicted with more than \SI{50}{\percent} accuracy
\citep{Pagolu2016a}.

\citet{Malkiel2003} noted that with the beginning of the new millennium, financial economists believed that stock prices are at least partly predictable.
They emphasized the behavioral and psychological elements of stock price determination.

Nowadays many internet users are microblogging.
Millions of messages are published daily on popular websites which provide microblogging services, such as Twitter, Tumblr and Facebook.
These published messages describe the personal life, opinions or current issues.
The more users post about products and services they use, the more microblogging websites become a valuable source of peoples' opinions and sentiments.
Therefore, this data can be used for marketing, social studies and as a measure of public opinion
\citep{Patodkar2016a, Pagolu2016a}. 
Most Twitter messages have a maximum length of 140 characters and represents the public opinion on a precise topic
\citep{Pagolu2016a}.

Combining these two research fields (namely \ac{EMH} and Twitter) should enable us to investigate whether stock prices can be predicted via public opinions on Twitter.

\section{Research Goals}
\label{s:introduction-researchgoals}

According to the factors presented in \cref{s:introduction-motivation} the central research question can be formulated:
\emph{To what extent can stock market movements be explained by the public opinion extracted from Twitter?}

The goal of this research is to analyze the correlation between the sentiment of tweets and the share movement of automotive companies.
This goal will be met by achieving the following objectives:

\begin{itemize}
    \item \textbf{G1} - Determine companies, keywords and stock symbols to analyze
    \item \textbf{G2} - Gather tweets and their sentiments and stock prices
    \item \textbf{G3} - Comparing sentiment time series with share prices
\end{itemize}

Based on the definitions of goals and having the central question in mind, the following sub tasks are defined in the form of questions in order to fulfill the goals:

\begin{itemize}
    \item \textbf{G1-Q1} - Which companies should be analyzed?
    \item \textbf{G1-Q2} - Which keywords should be used to find corresponding tweets?
    \item \textbf{G1-Q3} - Which company uses which stock symbol in order to retrieve share prices?
    \item \textbf{G2-Q4} - Why Twitter and not any other social media platform?
    \item \textbf{G2-Q5} - In which way can tweets be collected?
    \item \textbf{G2-Q6} - In which way can sentiments be determined?
    \item \textbf{G2-Q7} - Which sentiments are present for various companies?
	\item \textbf{G3-Q8} - Can the time series of sentiments explain the share prices?
\end{itemize}

\section{Research Methodology}
\label{s:introduction-researchmethodology}

The research follows a structure deducted from ``evaluation techniques for systems analysis and design modelling methods'' by \citet{Siau2011} in which the authors try to show the benefits and the shortcomings of different methods.
In the following the three main categories and their mapping to this thesis are shown:

\begin{description}
	\item[The \emph{theoretical and conceptual inquiry}]
		establishes the theoretical background of this thesis.
		Through literature research definitions and types of stock market prediction, option mining and social networks are found.
	
	\item[The \emph{case study}]
		is needed to capture tweets on the internet.
		This is done by using a \ac{DMITCAT} installation
		\citep{Borra2014}.
	
	\item[The \emph{metrics analysis}]
		is used to compare the results of the case study with share prices of the automotive companies.
\end{description}

As this thesis covers sentiments of people in a global context which are then compared to share prices in an economic context it can be classified as social science \citep{Recker2013}.
In the following the research actions which will be undertaken to answer the questions and fulfill the goals are explained.

\begin{itemize}
	\item To find answers to the questions \textbf{Q1} to \textbf{Q5} literature research will be conducted.
	A keyword search will be performed on the literature search engine \emph{Google Scholar}.
	Furthermore, the library will be searched as well.
	The retrieved literature is reviewed and, based on the references, new literature is obtained.
	
	\item With the theoretical background which has been obtained in answering the questions \textbf{Q1} to \textbf{Q6} a tweet collection system has been set up in order to answer the question \textbf{Q7}.
	This is done by setting up an open source tweet capturing system (\ac{DMITCAT}) and evaluating the sentiment of the captured tweets.
	
	\item Question \textbf{Q8} is answered through both literature research, which has been collected for the questions \textbf{Q1} to \textbf{Q6}, and evaluated sentiments of the collected tweets for question \textbf{Q7}.
\end{itemize}

\section{Structure of this Thesis}
\label{s:introduction-structureofthisthesis}

This section is followed by the background \cref{c:background}, where the necessary theoretical background will be explained. 
In \cref{c:casestudy}, the setup of tweet collection will be explained and the execution documented.
Afterwards, in \cref{c:analysis}, sentiments of collected tweets will be determined and converted into a time series which will then be compared to the time series of share prices.
Finally, in \cref{c:conclusion} the results of this work will be summed up, and limitations and further points of interest will be pointed out.